\title{Benchmarking Hadoop and Spark}


\author{Min Chen}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{School of Informatics, Computing, and Engineering}
  \city{Bloomington}
  \state{IN}
  \postcode{47408}
}
\email{mc43@iu.edu}

\author{Gregor von Laszewski}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{Smith Research Center}
  \city{Bloomington}
  \state{IN}
  \postcode{47408}
}
\email{laszewski@gmail.com}

\author{Bertolt Sobolik}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{School of Informatics, Computing, and Engineering}
  \city{Bloomington}
  \state{IN}
  \postcode{47408}
}
\email{bsobolik@iu.edu}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{M. Chen, G. v. Laszewski, B. Sobolik}


\begin{abstract}
\TODO{Add data set used}
Hadoop clusters are created on five networked Raspberry Pi 3 model B
computers. The aim is to create the cluster in a repeatable and
scalable fashion, automating as much of the setup process as
possible. Hadoop is deployed and configured to run as Docker
containers and directly on the operating system. Configurations are
tested to compare Docker against direct installation. Hadoop is also
configured in Docker and natively on Futuresystems Echo and similar
performance tests are done to compare the performance of the
configuration on Echo against that of the Pis.
\end{abstract}

\keywords{hid-sp18-419, hid-sp18-405, Hadoop, Raspberry, Pi}


\maketitle

\section{Introduction}
\TODO{Write an introduction.}


\section{Technology Used}
\TODO{Decide whether to use six pis or 5 pis and the screen. If the former, the hardware description below will need to change. We could use the sixth pi in the other cluster we made and create a cluster of 11.}
The hardware used for the Raspberry Pi cluster consists of:

\begin{itemize}
\item Five Raspberry Pi 3 Model B computers
\item One Waveshare 4'' HDMI LCD touchscreen
\item One Netgear model GS308 8-Port Gigabit ethernet switch
\item One Anker PowerPort 6 USB power supply
\item One Powtech 125V AC 15A 1875w adaptor with switch
\item Five 1' ethernet cables
\item Five 32 GB microSDHC UHS-I cards
\item Six 6'' USB 2.0 A-Male to Micro B cables
\end{itemize}

\TODO{Describe Echo.}
\TODO{Describe Hadoop.}
Docker is a technology that allows applications to run in containers
instead of full VMs. It leverages control groups and name space
isolation in the Linux kernel. Containers start up much faster than
VMs and is supported by all the major public cloud
vendors~\cite{Foster:2017:CCS:3158276}. The most current stable
release of Docker Community Edition was used for this project
(18.03.0-ce).


\section{Deployment}
To configure the Raspberry Pis, first SD cards were burned using a
script that takes start and end machine id numbers as an input. The
option to perform DHCP setup can be enabled with a flag. If DHCP is
not used, the script assigns static IPs to each machine.

\section{Data}
\TODO{Describe data}


\section{Benchmarking Process}
\TODO{Describe MapReduce task used for benchmarking.}


\section{Results}
\TODO{Add results.}

\begin{table}[hbt]
\centering
\caption{Benchmarking results}\label{t:results-table}
\begin{tabular}{llll}
Platform    & Docker & Deployment time & MapReduce Time \\
Pi 5 nodes  & Yes    & TBD             & TBD            \\
Pi 5 nodes  & No     & TBD             & TBD            \\
Echo        & Yes    & TBD             & TBD            \\
Echo        & No     & TBD             & TBD            \\
\end{tabular}
\end{table}



\section{Conclusion}

\TODO{Put here an conclusion. Conclusion and abstracts must not have any
citations in the section.}


\begin{acks}

  The authors would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report}
